Implementing Real-Time Transport Services over an Ossified Network

### 2016-06-23 paper.tex
Addresses point 2 in review #25B

In order to maintain compatibility with middleboxes, offering partial
reliability requires using \emph{inconsistent retransmissions}. This means
that the mapping between message data and TCP sequence numbers is no longer
static: a given TCP sequence number may be relate to different messages at
different times. Therefore, an application-level sequence number is
required to allow messages to be uniquely identified.
\todo{Review B: Inconsistent retransmissions are not well introduced. Should
be more explicit, and earlier.}

>>>>

Middleboxes in the network have ossified around TCP's reliability
mechanism: they do not expect gaps in the TCP sequence number space.
Honda \emph{et al.} \cite{honda:2011:extend-tcp} test the behaviour of
middleboxes in response to gaps in the TCP sequence number space, showing
that middleboxes interfere with flows in up to 29\% of tested paths. This
depends on the mechanism and port number used, with ports used by common
applications impacted most. To ensure compatibility with these middleboxes,
offering partial reliability requires using \emph{inconsistent
retransmissions}. Retransmissions will be triggered as under standard TCP
to ensure that the sequence number space is filled, but the data in a
retransmitted segment may not be the same as the original. This means that
the mapping between message data and TCP sequence numbers is no longer
static: a given TCP sequence number may be relate to different messages at
different times. Therefore, an application-level sequence number is
required to allow messages to be uniquely identified.
